%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Adam Shand}{}

\position{Environmental Data Scientist}
\address{Townsville, Australia}

\email{\href{mailto:adamshand22@gmail.com}{\nolinkurl{adamshand22@gmail.com}}}
\github{add-am}
\linkedin{adamshand}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {June, 2023}
    {Adam Shand~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{employment}{%
\section{Employment}\label{employment}}

\begin{cventries}
    \cventry{Technical Officer}{Dry Tropics Partnership For Healthy Waters (DTPHW)}{Townsville, Australia}{Apr. 2022 - Present}{\begin{cvitems}
\item Collaborated with industry, government, NGOs, and community stakeholders to deliver environmental monitoring reports.
\item Implemented the ANZECC (2000) and Environmental Protection Policy water quality guidelines for a range of monitoring projects.
\item Analysed multiple environmental indicators including climate data, water quality data, vegetation surveys, and fauna surveys.
\item Developed automated workflows for tasks such as data cleaning, manipulation, analysis, and visualisation.
\item Worked extensively with spatial data (rasters, vectors), flat files (spreadsheets, Excel), and 3-dimensional data (topography, hypercubes).
\item Engaged in public outreach and communication by delivering presentations at events, lecturing at JCU, and running stalls at community days.
\end{cvitems}}
    \cventry{Research Assistant}{Griffith University}{Gold Coast, Australia}{Nov. 2018 - Jan 2022}{\begin{cvitems}
\item Developed and applied tools for monitoring and resource assessment in marine and estuarine environments.
\item Utilised advanced data analysis, data management, coding, and automation techniques for multiple scientific publications.
\item Designed and presented complex technical and scientific reports to collaborators and stakeholders.
\item Served as a project manager for multiple desktop and in-field studies.
\item Supervised and provided guidance to a team of 7 undergradutate students and interns.
\end{cvitems}}
\end{cventries}

\hypertarget{education-and-awards}{%
\section{Education and Awards}\label{education-and-awards}}

\begin{cventries}
    \cventry{BSc (Hons) in Marine Science}{Griffith University}{Gold Coast, Australia}{Feb. 2020 - Nov. 2020}{\begin{cvitems}
\item Recipient of the Academic Excellence Award (2020).
\item First Class Honours with Distinction (GPA 7.0).
\item Honours research project was to develop an automated image recognition and indentification system for estuarine fish species.
\item Studied units including Scientific Data Analysis, Scientific Report Writing, and Research Planning
\end{cvitems}}
    \cventry{BMarSc in Marine Ecology}{Griffith University}{Gold Coast, Australia}{Feb. 2017 - Nov. 2019}{\begin{cvitems}
\item Recipient of the Academic Excellence Award (2017, 2018, 2019).
\item Graduate with Distinction (GPA 6.5).
\item Mentor for the Griffith University Science Stream (2019).
\item Capstone project was to assess the impact of soft coral allelopathy on surrounding hard coral cover.
\item Studied units including Applied Data Science, Environmental Chemistry, Ecotoxicology, and Estuarine Ecology.
\end{cvitems}}
\end{cventries}

\hypertarget{qualifications}{%
\section{Qualifications}\label{qualifications}}

\begin{cvhonors}
    \cvhonor{}{HLTAID011 - Provide First Aid}{ABC First Aid}{2023}
    \cvhonor{}{HLTAID010 - PRovide basic emergency life support}{ABC First Aid}{2023}
    \cvhonor{}{HLTAID009 - Provide cardiopulmonary resuscitation}{ABC First Aid}{2023}
    \cvhonor{}{Aquatic Environment Monitoring Skills}{JCU, TropWater}{2023}
    \cvhonor{}{Drone Pilot (RPA Operator Accreditation)}{CASA}{2023}
    \cvhonor{}{Lifetime Member of the Golden Key International Honour Society}{Griffith University}{2018}
    \cvhonor{}{Recreational Boat License}{DTMR, QLD}{2017}
    \cvhonor{}{Advanced Open Water Diver}{PADI}{2016}
    \cvhonor{}{Certificate I in Maritime Operations (MAR10313)}{TAFE, NSW}{2015}
    \cvhonor{}{Class C and Class RE Manual Drivers License}{DTMR, QLD}{2015}
\end{cvhonors}



\end{document}
